### 2018-05-17 Sections/essay_the_quantum_space_race.tex
Multiplexed detector eqn and fig

At the time of writing this book the world's first quantum-capable satellite was very recently launched into low-Earth orbit by the Chinese. The key capability of the satellite was to distribute entangled pairs of photons to ground stations thousands of kilometres apart. Using these entangled pairs, quantum key distribution was demonstrated, allowing theoretically unbreakable cryptography between the ground stations that no eavesdropper could compromise, guaranteed by the laws of physics.

@@

The first generation satellite that was recently developed merely contained an entanglement source, and satellite-to-ground optical links via telescopes armed with laser tracking (see Fig.~\ref{fig:first_gen_sat}). However, this prototype is strictly restricted to distributing entanglement between two ground stations, both simultaneously in line-of-sight of the satellite.

@@

To facilitate a true global network, the next generation of satellites will need to form a constellation sufficiently dense that every point on the Earth's surface is always within line of sight of at least one satellite (see Fig.~\ref{fig:sat_honeycomb}).

@@

To enable a constellation, the satellites will need satellite-to-satellite links in addition to the satellite-to-ground links, such that they can relay the entanglement around the curvature of the Earth to overcome line-of-sight limitations. Additionally, they will need to do more than just prepare entangled states, but also perform entangling measurements, such that they can be configured as a quantum repeater network. A concept model for a next generation satellite with these essential capabilities is shown in Fig.~\ref{fig:next_gen_sat}.

@@

While the next generation satellite appear only incrementally more complex than the first generation ones, it is in fact far more technologically challenging. The main obstacle is that when performing entangling measurements, photons must arrive at the detector simultaneously. Obviously this is hard to enforce in space over long distances on fast-moving objects. Therefore quantum memories will be required, such that the first of two arriving photons is held in memory until the second one arrives, at which point it is read out from memory and the two photons are jointly measured. Unfortunately, such quantum memories are still very much in their infancy, and not reliable enough or of sufficient quality that they are ready for prime-time applications like a global space-based repeater network. It is unclear how far off these technologies are.

@@

The Chinese have successfully launched and demonstrated the first quantum satellite. This marks the beginning of the quantum space race. Who will respond? For he who achieves a global network first will wield a huge competitive advantage in the upcoming era of the quantum internet and all its foreseeable and unforeseeable applications.

>>>>

At the time of writing this book the world's first quantum-capable satellite was very recently launched into low-Earth orbit by Chinese scientists \cite{JWP}. The key capability of the satellite was to distribute entangled pairs of photons to ground stations thousands of kilometres apart. Using these entangled pairs, quantum key distribution was demonstrated, allowing theoretically unbreakable cryptography between the ground stations that no eavesdropper could compromise, guaranteed by the laws of physics.

@@

The first generation satellite that was recently developed merely contained an entanglement source, and satellite-to-ground optical links via telescopes armed with laser tracking (Fig.~\ref{fig:first_gen_sat}). However, this prototype is strictly restricted to distributing entanglement between two ground stations, both simultaneously in line-of-sight of the satellite.

@@

To facilitate a true global network, the next generation of satellites will need to form a constellation sufficiently dense that every point on the Earth's surface is always within line of sight of at least one satellite (Fig.~\ref{fig:sat_honeycomb}).

@@

To enable a constellation, the satellites will need satellite-to-satellite links in addition to the satellite-to-ground links, such that they can relay the entanglement around the curvature of the Earth to overcome line-of-sight limitations. Additionally, they will need to do more than just prepare entangled states, but also perform entangling measurements, such that they can be configured as a quantum repeater network. A concept model for a next-generation satellite with these essential capabilities is shown in Fig.~\ref{fig:next_gen_sat}.

@@

While the next-generation satellite may appear only incrementally more complex than the first generation one, it is in fact far more technologically challenging. The main obstacle is that when performing entangling measurements, photons must arrive at the detector simultaneously. Obviously this is hard to enforce in space over long distances on fast-moving objects. Therefore quantum memories will be required, such that the first of two arriving photons is held in memory until the second one arrives, at which point it is read out from memory and the two photons are jointly measured. Unfortunately, such quantum memories are still very much in their infancy, and not reliable enough or of sufficient quality that they are ready for prime-time applications like a global space-based repeater network. It is unclear how far off these technologies are.

@@

The Chinese have successfully launched and demonstrated the first quantum satellite. This marks the beginning of the quantum space race. Who will respond? For he who achieves a global network first will wield a huge competitive technological advantage in the upcoming era of the quantum internet and all its foreseeable and unforeseeable applications.

### 2018-05-17 Sections/protocols_for_the_quantum_internet.tex
Essay - space race
Minor restructure
Multiplexed detector eqn and fig

Furthermore, photo-detectors are subject to `dead-time'\index{Dead-time}, which renders them inactive for a finite recovery period following a detection event. This is of especial importance in time-bin-encoded schemes (Sec.~\ref{sec:time_bin}), where detectors must resolve photons over very short timescales on the order of nanoseconds.

@@

Mathematically, we are interested in the probability \mbox{$P(n_\text{meas}=n_\text{inc})$} that the measured number of photons ($n_\text{meas}$) matches the actual number of incident photons ($n_\text{inc}$). The structure of this expression will vary enormously depending on the details of the architecture (e.g multi-port interferometer vs fibre-loop). However, \cite{rohdeHuntington} presented a very general mathematical formalism applicable to all architectural variants. The simplest case to consider is the multi-port interferometer, owing to its perfect symmetry. The probability is simply the probability that no output mode from the multi-port contain multiple photons. %A quick calculation yields,
%\begin{align}
%	P(n_\text{meas}=n_\text{inc}) = \binom{m}{n_\text{inc}}\left(\frac{\eta}{m}\right)^{n_\text{inc}},
%\end{align}
%not accounting for other lesser errors such as dark-counts.

%\comment{Check this}

@@

>>>>

Furthermore, photo-detectors are subject to `dead-time'\index{Dead-time}, which renders them inactive for a finite recovery period following a detection event. This is of especial importance in time-bin-encoded schemes (Sec.~\ref{sec:time_bin}), where detectors must resolve photons over very short timescales on the order of nanoseconds. Dead-time can be modelled as a time-dependent efficiency of the form,
\begin{align}
\eta(t) = \left\{\begin{array}{cc}
 0, & t<\tau_\text{dt} \\
 \eta_\text{ss}, & t\geq\tau_\text{dt} \\
\end{array}\right.,
\end{align}
where $t$ is time, $\tau_\text{dt}$ is the detector's deadtime, and $\eta_\text{ss}$ is the detector's steady-state efficiency (i.e when not dead).

@@

Mathematically, we are interested in the probability \mbox{$P(n_\text{meas}=n_\text{inc})$} that the measured number of photons ($n_\text{meas}$) matches the actual number of incident photons ($n_\text{inc}$). The structure of this expression will vary enormously depending on the details of the architecture (e.g multi-port interferometer vs fibre-loop). However, \cite{rohdeHuntington} presented a very general mathematical formalism applicable to all architectural variants. The simplest case to consider is the multi-port interferometer, owing to its perfect symmetry. The probability is simply the probability that no output mode from the multi-port contain multiple photons. A quick calculation yields,
\begin{align}
	P(n_\text{meas}=n_\text{inc}) = \frac{m!}{(m-n)!m^n},
\end{align}
not accounting for other lesser errors such as dark-counts. This is shown in Fig.~\ref{fig:multiplexed_pd}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{multiplexed_detector}
	\caption{Probability of a multiplexed detector inferring the correct number of photons with $n$ incident photons across $m$ balanced modes. The detectors have perfect efficiency, \mbox{$\eta=1$}. $n$ ranges from $1$ (top) to $5$ (bottom). All curves asymptotically approach \mbox{$P_n=1$} for large $m$.}\label{fig:multiplexed_pd}
\end{figure}
